\section{Introduction}

% What is the problem (stroke eburden)

Stroke remains one of the top three global causes of death and disability \cite{feigin_global_2021}. Despite reductions in age-standardised rates of stroke, ageing populations are driving an increase in the absolute number of strokes \cite{feigin_global_2021}. Across Europe, in 2017, stroke was found to cost healthcare systems \texteuro 27 billion, or 1.7\% of health expenditure \cite{luengo-fernandez_economic_2020}.

Intravenous thrombolysis (IVT) and mechanical thrombectomy (MT) are two well-established treatments for reduction or removal of clots causing ischaemic stroke, reducing disability caused by stroke, but both lose effectiveness in the hours following a stroke \cite{emberson_effect_2014, fransen_time_2016}. IVT is suitable for both non-large vessel occlusions (nLVO) and large vessel occlusions (LVO). MT is suitable only for LVO, but has superior efficacy compared to IVT.

% What do we know (see chen_systematic_2022 for review)

As a way of improving time from onset to IVT, mobile stroke units (MSUs) were first proposed in 2003 by Fassbender et al. \cite{fassbender_mobile_2003}. An MSU is a bespoke ambulance that contains the required technology and specialist opinion for diagnosing ischaemic stroke and making an IVT treatment decision, i.e. a computed tomography (CT) scanner and an in-person or telemedicine review by a stroke specialist \cite{taqui_reduction_2017}. MSUs were first trialled in Homberg, Germany \cite{walter_diagnosis_2012} and have been introduced based on MT-capable centres (comprehensive stroke centres, CSCs) in other health systems. No health system has yet deployed MSUs at a regional or country-wide level.

Fatima \textit{et al}. \cite{fatima_mobile_2020} have published a meta-analysis of MSU trials. They reviewed evidence from a total of 21,297 patients from 11 publications (seven randomized controlled trials and four non-randomized controlled trials including prospective cohort studies). Mean time to IVT was reduced by 12 minutes on average, from 75 to 63 minutes. In a pooled analysis they found the odds of a good outcome (modified Rankin Scale, mRS, 0--2 at day 7) were improved 1.46 times by use of an MSU.

In a separate meta-analysis, Chen \textit{et al.} \cite{chen_systematic_2022} reviewed evidence from a total of 22,766 patients from 16 publications. In total 7,682 (33.8\%) were treated in the MSU and 15,084 (66.2\%) with usual care. They found higher use of IVT in the MSU group (37.3\% vs. 27.7\%), and an improvement in the proportion of patients with mRS 0--2 at 90 days (66.2\% vs 58.8\%).  The pooled analysis of time metrics indicated a mean reduction of 33 minutes in time to IVT between MSU and usual care.

Turc \textit{et al.} \cite{turc_comparison_2022} conducted a further meta-analysis that reviewed evidence from 14 studies. They found that MSUs increased the odds of a better outcome by 1.64 (adjusted odds ratio), with a median reduction in time to IVT of 31 minutes and an increase in odds of receiving IVT of 1.83 (unadjusted odds ratio). The odds of receiving IVT in the first 60 minutes after stroke (the golden hour) were increased by 7.71 (unadjusted odds ratio).

There is less known about how MSUs affect use, and speed, of MT, where the main advantage of use of a MSU with CT-A would be direct transfer of the patient to a MT-capable centre (avoiding inter-hospital transfers with their associated delays). A review of available evidence suggests there is an evidence gap in MSUs and MT, as in many trials the MSU were dispatched from CSCs, into populations which would have been directly admitted under usual care \cite{navi_mobile_2022}. In Berlin, Ebenger \textit{et al.} \cite{ebinger_association_2021} found that the MT rate and speed were essentially unchanged (13. 8\% vs 14. 2\%, and the median dispatch to MT 137 min vs 125 min, for MSU and usual care). In the BEST Study \cite{grotta_prospective_2021} median time from 911 alert to MT was 141 and 132 minutes for MSU and usual care. The BEST-MSU substudy \cite{czap_impact_2024} was a subset of the BEST study, for IVT-eligible stroke patients with LVO MT rates were 79\% and 86\% for MSU and usual care,  with median alert-to-puncture times of 142 min and 132 min. In general, in that study, for patients with LVO stroke eligible for IVT, though MT was delivered a little later, MSU management was associated with better clinical outcomes compared to standard management, with an adjusted odds ratio of having mRS 0-1 of 2.60. Helwig \textit{et al.} \cite{helwig_prehospital_2019} showed the potential of MSUs for improved triage of patients to the correct type of hospital (providing MT or not). Compared to the Los Angeles Motor Scale (LAMS), MSUs had a triage accuracy of 100\% compared to about 70\% for LAMS. MSUs equipped with CT Angiogram (CT-A) were also found to significantly improve MT workflows at the receiving hospital, reducing door-to-puncture times from 94 to 43 minutes \cite{czap_mobile_2020}.

% What do we not know (Impact in England, Demographics, Geography)

MSU trials have generally been in metropolitan areas, where the MSU can respond rapidly to suspected stroke and travel times are relatively short. In order to predict the benefit of MSUs for patients with suspected LVO across a broader geographic area, Holodinsky et al. \cite{holodinsky_jessalyn_k_what_2020} used modelling to predict the benefit, from IVT and MT, of using MSUs to cover larger distances (up to 4.5 hours travel for the MSU, to include all people who might receive IVT). They found that the effect of MSUs was likely to be minimal in the regions close to the stroke centre that was the MSU base. They predicted no more than 1 percentage point increase in the proportion of patients with an outcome of mRS 0--2, but this could rise to about a 2 percentage point increase in a halo further away from the stroke centre where the MSU made the difference between receiving IVT or not.

% What are our aims here? 

Our work aimed to model the effect of MSUs on the likely times to both IVT and MT (including modelling inter-hospital transfers when required) and to estimate outcomes both as the proportion with mRS 0--2 at 6 months and their corresponding health utility. We modelled these effects across  all of England (population 58 million in 2023) performing a detailed geographic analysis at the Lower Super Output Areas (LSOA) level. We performed a comprehensive analysis of the effect of changing process times for usual care and MSU care. We also investigated how the number of MSU base locations affects IVT/MT times and resulting patient outcomes.